### 2019-02-08 tex_v2/manuscript.tex
file cleanup

		\change{maybe edit, move to conclusions, or just delete this paragraph}Below we demonstrate that the endocuticle does not vary in tensile strength across the rostrum or between species, making it unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum.
		The available evidence therefore suggests that the relative flexibility of the snout is primarily derived from the composite profile of its cuticle.

	\section{Force-controlled loading to fracture}
	%475 words, try to keep around this length
		To better characterize the mechanical behavior of the snout as an integrated whole, we performed tensile testing on the snouts of six species in the genus \textit{Curculio}, representing a mixture of closely and distantly related taxa.
		Although the heads were rehydrated by immersion in de-ionized water for 24 hours, we observed comparatively brittle fracture (but see below), in contrast to GIVE EXAMPLES HERE.
		The tensile behavior for the cuticle of these weevils is a result of its microstructure, which lacks pores, etc (give reasons).
		THIS IS ALSO A GOOD SPOT TO SIGNPOST WHAT I FOUND IN GENERAL.

		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
		Consequently, there was a negative correlation between utlimate tensile strenth of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture, indicating that as the proportion of exocuticle increased, tensile strength decreased.
		In other words, UTS is strongly correlated with the cross-sectional area of the endocuticle across species.
		These associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

		These data have three important implications:
		\begin{enumerate}
			\item There is very little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology. (singh 2016, jansen 2016)
			\item The endocuticle contributes more to the tensile strength of the rostrum than the exocuticle, possibly because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
			\item Thus, in addition to making the cuticle more flexible, the altered apical composite profile makes it less likely to break, suggesting a possible means by which the system evolved (via negative selection of breakage, maybe say this in conclusions).
		\end{enumerate}

		Finally, we observed that the elastic modulus is higher in specimens with a longer snout.
		This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) would need to be more flexible to avoid fracture during oviposition.
		Based on preliminary confocal microscopy data, we speculate that this phenomenon may be the result of a longer scrobe/transition/gradient from the basal profile to the apical profile in longer rostra.
		A decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.
		[OR SAY MORE CONCISELY THAT: based on prelim CLSM data we believe that the snout is reinforced against bucking with thicker exocuticle in the base of these species; as a result, the higher volume fraction of exocuticle in the snout increases young's modulus for such species]

@@

	\section{Fractography of test specimens}
	%currently ~400 words, keep to this length
		Examination of the fracture surfaces and adjacent cuticle of tensile testing specimens revealed that although fracture was comparatively brittle, the fracture mechanics of the exocuticle and endocuticle differed according to their microstructure, in agreement with previous studies (name some).

>>>>

	\section{Force-controlled loading to fracture}
	%550 words, maybe reduce?? Still must add numbers...

		To better characterize the mechanical behavior of the snout as an integrated whole, we performed tensile testing on the snouts of six species in the genus \textit{Curculio}, representing a mixture of closely and distantly related taxa.
		Although the heads were rehydrated by immersion in de-ionized water for 24 hours, we observed comparatively brittle fracture (but see below), in contrast to GIVE EXAMPLES HERE.

		In general, the behavior of the rostrum is non-linear viscoelastic, and, as in other biological materials, exhibits a stress-strain curve characterized by a steady increase in stiffness, beginning with a toe-in region and terminating in apparently brittle fracture after a period of strain hardening.
		We observed that the maximum force sustained at the site of the break was strongly correlated with the cross-sectional area of the endocuticle, and not the exocuticle.
		Consequently, there was a negative correlation between utlimate tensile strength of the specimen and the ratio of exocuticle to endocuticle cross-sectional area at the site of fracture.
		In other words, UTS is positively correlated with the relative proportion of the endocuticle across species.

		Although the proportion of exocuticle is predicted to be positively correlated with the stiffness of the resulting composite, we found no such associations because of the anterior-posterior gradient in cuticle profile.
		Because the cross-sectional areas of the cuticle regions vary across the length of the head, it is meaningless to attempt to correlate these areas to properties of the entire snout.
		Instead, we found that the uniaxial elastic moduli of the snout under low strain (E-low) was inversely correlated with the ultimate strain and toughness of the snout (as was the secant modulus, E-sec).
		These associations were found to be statistically significant and independent of species membership, rostrum length, and location on the snout.

		From our results, we infer that there is little variation in the gross elastic behavior of the cuticle across the genus, in agreement with our current understanding of cuticle mechanobiology, making it unlikely that differences in sclerotization or chitin composition within the cuticle are responsible for the mechanical behavior of the rostrum (singh 2016, jansen 2016).
		Furthermore, the endocuticle apparently contributes more to the tensile strength of the rostrum than the exocuticle, likely because the endocuticle is organized in large bundles of aligned, anisotropic fibers.
		Thus, in addition to making the cuticle more flexible, the altered apical composite profile makes the rostrum less likely to break, suggesting a possible means by which this system evolved\info{(via negative selection of breakage, maybe say this in conclusions)}.

		\info{DO I really want to discuss this? Occupies precious space...}Finally, we observed that the elastic modulus is higher in specimens with a longer snout.
		This observation was initially quite puzzling, as we had expected that a longer (and typically more strongly curved [insert ecomorph paper ref here]) would need to be more flexible to avoid fracture during oviposition.
		Based on preliminary confocal microscopy data, we speculate that this may be the result of a longer transition gradient from the basal profile to the apical profile in longer rostra.
		A decrease in exocuticle thickness along a longer portion of the base might reinforce the snout against buckling; however Young's modulus of the rostrum would be comparatively higher in these species because of the greater volume fraction of exocuticle.

@@

	\section{Fractography of test specimens}
	%currently ~400 words, keep to this length or reduce to 2 short paragraphs
		Examination of the fracture surfaces and adjacent cuticle of tensile testing specimens revealed that although fracture was comparatively brittle, the fracture mechanics of the exocuticle and endocuticle differed according to their microstructure, in agreement with previous studies (name some).
